Practical Machine Learning - Prediction Assignment
Feb 22, 2015
========================================================

## Data Retrieval, Cleaning and EDA

Load the need packages
```{r}
library(randomForest)
library(caret)
setwd("C:/Users/ed/Documents/Coursera/Course8_Machine Learning/Assignment")

```

Read in and check out and clean the data - iterative - had to take care of #DIV/0 - also to take care of the null values
```{r }
Data <- read.csv("pml-training.csv",na.strings=c('NA','','#DIV/0!'))
DataTwenty <- read.csv("pml-testing.csv",na.strings=c('NA','','#DIV/0!'))

View (Data)
#dim(Data);dim(DataTwenty)
#summary(Data)
#names(Data)
```

Let's delete the useless columns, first 7 columns of Ids and datetime are not useful in a model. Remember to provide the same treatment to the testing set.
Let's also get columns that are fully populated with Data

```{r}
Data1 <- Data[-(1:7)]
DataTwenty1 <- DataTwenty[-(1:7)]

goodcol <- colnames(Data1[colSums(is.na(Data1)) == 0])
goodcolTwenty <- colnames(DataTwenty1[colSums(is.na(DataTwenty1)) == 0])

Data2 <- Data1[goodcol]
DataTwenty2 <- DataTwenty1[goodcolTwenty]

View(Data2)
View(DataTwenty2)
```

## Modeling
Create a traing and testing for cross validation of the model. Let's try a RandomForest (try Rfit and it was bad - had to delete and forum the rest)

```{r}
set.seed(1345345)
inTrain = createDataPartition(Data2$classe, p = 3/4)[[1]]
training = Data2[inTrain,]
testing = Data2[-inTrain,]
```

## Cross Validation
```{r}
modFit2 <- randomForest(classe ~ .,data=training,ntree=500, mtry=30)

training_pred2 <- predict(modFit2,training)
print(confusionMatrix(training_pred2, training$classe))
```
HeeHaw! - this is 100% accurate on the training - 99% on testing.. gtg

```{r}
training_pred3 <- predict(modFit2,testing)
print(confusionMatrix(training_pred3, testing$classe))
```
I would say this model is ready for prime time


## Prediction
Now we can test this boy on the 20 real testing population

```{r}
answers <- predict(modFit2,DataTwenty2)
answers
```

From the results, the random Forest model was very effective and its predictions.  Getting a high accurancy.  The accurancy yield 20/20 in the Project submission as well


